### 2017-11-27 paper/sections/4_dynamic-policies.tex
paper: addresses #35, #44, #46
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Using the Mantle policy engine, we test a variety of cache management tools and
algorithms on the worker using the keyspace analysis in
Section~\S\ref{sec:parsplice-keyspace-analysis}.  The evaluation metric is the
accuracy and runtime of each strategy; the policy should be accurate enough so
as to sacrifice negligible performance and fast enough to run as often as we
want to detect key access patterns.  First we sized the cache according to our
system specific knowledge. By ``system", we mean the hardware and software of
the storage hierarchy. We look at request rate, unique keys in a sliding
window, and bandwidth capabilities. For example, we know that LevelDB cannot
handle high IO request rates.

% technical details
The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The middle graph shares the \(y\) axis and shows the trade-off of using a basic
LRU-style cache for different cache sizes, where the penalty for a cache miss
is retrieving the data from the persistent database.  We evict keys (if
necessary) at every operation instead of when segments complete because the
cache fills up too quickly otherwise. This is implemented using a ``when"
policy of \texttt{server[whoami]['cachesize']>n} and a ``how much" policy of
\texttt{servers[whoami]['cachesize']-n}.  The error bars are the standard
deviation of 3 runs.  Although the keyspace grows to 150K, a 100K key cache
achieves 99\% of the performance. Decreasing the cache degrades performance and
predictability.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
\caption{The performance and resource utilization trade-off for different cache
management policies. ``None" is ParSplice unmodified, ``Fixed Sized Cache"
limits the size of the cache by evicting the least recently used items, and
``Multi-Policy Cache" switches to a fixed sized cache after absorbing the
initial burstiness of the workload.  The size of the fixed sized cache for each
experiment is on the \(x\) axis.  \label{fig:methodology-tradeoff}}
\end{figure}
%
%\footnotesize \centering \begin{minted}[xleftmargin=3em,linenos]{lua} function
%when() if server[whoami]['cachesize'] > n then return true end return false
%end
%
%function howmuch() if servers[whoami]['cachesize'] > n return
%servers[whoami]['cachesize'] - n end return 0 end \end{minted} \caption{Policy
%that implements a basic LRU cache. The performance and memory utilization for
%different values of \(n\) are graphed in
%Figure~\ref{fig:methodology-tradeoff}.  \label{src:lru}} \end{figure}

% why is the performance lower for smaller caches?
But the top graph in Figure~\ref{fig:motivation-regimes} suggests that a
smaller cache size should suffice, as only 100 keys seem to be active at any
one time.  It turns out that the unique keys plotted in
Figure~\ref{fig:motivation-regimes} are per second and are not representative
of the actual active keyspace; the number of active keys is larger than 100, as
some keys may be accessed at time \(t_0\), not in \(t_1\), and then again in
\(t_2\). Because the cache is too small, reads and writes hit the persistent
database, where the excessive traffic triggers a LevelDB compaction and reads
block.  To avoid overloading the storage hierarchy with requests, we design a
multi-part policy that switches between:

@@

% results: same level of performance can be achieved 
The key observation is that small caches incur too much load on the persistent
database at the beginning of the run but should suffice after the initial read
flash crowd passes because the keyspace is far less active.  We program Mantle
to trigger the policy switch at 100K keys to absorb the flash crowd at the
beginning of the run. Once triggered, keys are evicted to bring the size of the
cache down to the threshold.  The actual policy is shown and described in more
detail in the next section in Figure~\ref{src:lru-dyn}.  The plot on the right
side of Figure~\ref{fig:methodology-tradeoff} shows the performance/utilization
trade-off of the multi-part policy, where the cache sizes for the \(n\) key
limit policy are along the \(x\) axis.  They show better performance than the
single \(n\) key policies. The performance and memory utilization for a 100K
key cache size is the same as the 100K bar in the ``Multi-Part Policy" graph in
Figure~\ref{fig:methodology-tradeoff} but the rest reduce the size of the
keyspace after the read flash crowd.  We see the worst performance when the
engine switches to the 10 key limit policy, which achieves 94\% of the
performance while only using 40KB of memory.

@@

The results in Figure~\ref{fig:methodology-tradeoff} are slightly deceiving for
two reasons: (1) segments take longer to generate later in the run and (2) the
memory footprint is the value at the end of 2.5 hours.  For (1), the trajectory
length vs.  wall-clock time curves down over time; as the nanoparticle grows
it takes longer to generate segments so by the time we reach 2 hours, over 90\%
of the trajectory is already generated.  For (2), the memory footprint rises
until we reach 100K key switch threshold at 0.4GB, as shown by the
``\(\Delta_1\), Multi-Policy" curve in Figure~\ref{fig:memory-vs-time} but in
Figure~\ref{fig:methodology-tradeoff} we plot the final value. As a result, we
can only conclude that this policy only works well for this 2.5 hour run.

% but the result is still valid
Despite these caveats, the result is still valid: we found a multi-policy cache 
management strategy that absorbs the cost of a high read throughput on a small
keyspace and reduces the memory pressure for a 2.5 hour run. Our experiments
show the effectiveness of the policy engine we integrated into
ParSplice, not that we were able to identify the best policy for all system
setups ({\it i.e.} different ParSplice parameters, number of worker tasks, and
job lengths).  To solve that problem, we need a way to identify what thresholds
we should use for different job permutations.

@@

\begin{figure*}[t!]
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
	\includegraphics[width=0.89\textwidth]{figures/keyspace-zoomed.png}\\
\caption{Key activity for a 4 hour run shows groups of accesses to the same
subset of keys. Detecting these access patterns leads to a more accurate cache
management strategy, which is discussed in
Section~\S\ref{sec:regime-detection}.\label{fig:keyspace-zoomed}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``No Cache Management" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload) , and
``Dynamic Policy" (sizes cache according to key access patterns).
\label{fig:memory-vs-time}}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{figures/dscache-vs-none.png}\\
	\caption{Performance/Utilization for dynamically sized cache (DSCache)
policy. With negligible performance degradation, DSCache adjusts to different
\(\Delta\)s over 2\(\times\) memory in the best case.
\label{fig:dscache-vs-none}}
    \end{subfigure}%
    \caption{Different cache management policies tested over the Mantle policy engine.}
\end{figure*}

@@

Figure~\ref{fig:keyspace-zoomed} shows which keys (\(y\) axis) are accessed by
tasks over time (\(x\) axis). The groups of accesses to a subset of keys occurs
because molecules are stuck in deep trajectories. Recall that the cache stores
the molecules' EOM minima, which is the smallest effective energy that a
molecule observes during its trajectory. So molecules stuck in deep
trajectories explore the same minima until they can escape to a new set of
states. This exploration of the same set of states is called a superbasin.  In
Figure~\ref{fig:keyspace-zoomed}, superbasins are never re-visited because the
simulation only adds molecules; we can never reach a state with less molecules.
This is why keys are never re-accessed.  Despite these patterns, the following
characteristics of superbasins make it hard to detect them:

Detecting these superbasins can lead to more effective cache management
strategies because the height of the groups of key accesses is ``how much" of
the cache to evict and the width of the groups of key accesses is ``when" to
evict values from the cache.  The zoomed portion of
Figure~\ref{fig:keyspace-zoomed} shows how a single superbasin affects the key
accesses. Moving along the \(x\) axis shows that the number of unique keys
accessed over time grows while moving along the \(y\) axis shows that early
keys are accessed more often.

@@

Below we describe the policies we implemented and deployed using Mantle.

@@

  \item Calculus: use derivative to strip away magnitudes; use large positive
slopes followed by large negative slope as signal for new set of key accesses.
``Zero-crossing", set to 40 seconds, for distance between small/large spikes to
avoid false positives; `window size", set to 200 seconds, for the size of the
moving average

  \item K-Means Clustering fails because ``K" is not known {\it a-priori} and
groups of key accesses are different size. ``K", set to 4, for the number of clusters in the data
using the sum of the distances to the centroid

  \item DBScan: finds clusters using density as a metric. ``Eps", set to 20, for
max distance between 2 samples in same neighborhood; ``Min", set to 5, for the
number of samples per core

  \item Anomaly Detection: size of the image is too big and bottom edges are
not thick enough

@@

After trying these techniques we found that the basic algorithm in
Figure~\ref{src:dyn-cache} works best. The algorithm detects groups of key
access patterns, which we call ``fans", by iterating backwards through the key
access trace, finding the lowest key ID, and comparing against the lowest key
ID we have seen so far (Line 7). We also maintain the top and bottom of each
group of key accesses (Line 13) so we can tell the ``how much" policy the
number of keys to evict (Line 19).  The algorithm iterates backwards over the
key access trace because a change in the minimum value signals a new group of
key accesses. No signal exists iterating left to right, as the maximum value
always increases and the minimum values at the bottom of each group of key
accesses are sparse.  For example, the maximum distance between values along
the bottom edge of the zoomed group of key accesses in
Figure~\ref{fig:keyspace-zoomed} is 125 seconds, while the maximum distance
between minimum values for the group of key accesses before is 0 seconds. As a
result of this sparseness, iterating left to right requires a ``window size"
parameter to determine when we think a minimum value will not show up again.
We exchange runtime, in the form of an O(\(n\)) algorithm where \(n\) is the
number events, for simplicity because this approach avoids adding new
thresholds for key access pattern detection ({\it e.g.}, space between key
accesses, space between key IDs, and window size of consecutive key accesses).

@@

\begin{figure}[h]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
d = timeseries()          -- provided by mantle
ts, id = d:get(d:size())  -- provided by mantle
fan  = {start=nil, finish=ts, top=0, bottom=id}
fans = {}
for i=d:size(),1,-1 do    -- detect all fans
  ts, id = d:get(i)
  if id < fan['bottom'] then
    fan['start']  = ts
    fans[#fans+1] = fan 
    fan = {start=nil, finish=ts, top=0, bottom=id}
  end

  if id > fan['top'] then fan['top'] = id end 
end
fan['start'] = 0 
fans[#fans+1] = fan

if #fans < 2 then return false else
  WRstate(fans[#fans-1]['top']-fans[1]['bottom'])
  return true
end
\end{minted}
\caption{The dynamically sized cache policy, whose performance is shown in 
Figure~\ref{fig:cache-management}, iterates backwards over timestamp-key pairs
and detects when key accesses move on to a new subset of
keys. We refer to groups of key accesses as ``fans".\label{src:dyn-cache}}
\end{figure}

>>>>

Using the Mantle policy engine, we test a variety of cache management tools and
algorithms on the worker using the keyspace analysis in
Section~\S\ref{sec:parsplice-keyspace-analysis}.  Our evaluation uses the total
``trajectory length" as the goodness metric. This value is the duration of the
overall trajectory produced by ParSplice. At ideal efficiency, the trajectory
length should increase with the square root of the wall-clock time, since the
wall-clock cost of time-stepping the system by one simulation time unit
increases in proportion of the total number of atoms.  The policy should avoid
reducing the trajectory length and be fast enough to run as often as we want to
detect key access patterns.  First we sized the cache according to our system
specific knowledge, {\it i.e.} the hardware and software of the storage
hierarchy such as request rate, unique keys in a sliding window, and bandwidth
capabilities.

% technical details
The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The middle graph labeled "Fixed Cache Size" shares the \(y\) axis and shows the
trade-off of using a basic LRU-style cache for different cache sizes, where the
penalty for a cache miss is retrieving the data from the persistent database.
We evict keys (if necessary) at every operation instead of when segments
complete because the cache fills up too quickly otherwise. This is implemented
using a ``when" policy of:

\begin{figure}[h]
\footnotesize
\begin{minted}{lua}
server[whoami]['cachesize']>n
\end{minted}
\end{figure}

and a ``how much" policy of:

\begin{figure}[h]
\footnotesize
\begin{minted}{lua}
servers[whoami]['cachesize']-n
\end{minted}
\end{figure}

The error bars are the standard deviation of 3 runs.  Although the keyspace
grows to 150K, a 100K key cache achieves 99\% of the performance. Decreasing
the cache degrades performance and predictability.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
\caption{Policy performance/utilization: ``None" is ParSplice unmodified,
``Fixed Sized Cache" evicts keys using LRU , and ``Multi-Policy Cache" switches
to fixed sized cache after absorbing the workload's initial burstiness.  Fixed
sized caches are on the \(x\) axis.\label{fig:methodology-tradeoff}}
\end{figure}

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``No Cache Management" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload) , and
``Dynamic Policy" (sizes cache according to key access patterns).
\label{fig:memory-vs-time}}
\end{figure}%

%
%\footnotesize \centering \begin{minted}[xleftmargin=3em,linenos]{lua} function
%when() if server[whoami]['cachesize'] > n then return true end return false
%end
%
%function howmuch() if servers[whoami]['cachesize'] > n return
%servers[whoami]['cachesize'] - n end return 0 end \end{minted} \caption{Policy
%that implements a basic LRU cache. The performance and memory utilization for
%different values of \(n\) are graphed in
%Figure~\ref{fig:methodology-tradeoff}.  \label{src:lru}} \end{figure}

% why is the performance lower for smaller caches?
But the top graph in Figure~\ref{fig:motivation-regimes} suggests that a
smaller cache size should suffice, as only 100 keys seem to be active at any
one time.  It turns out that the unique keys plotted in
Figure~\ref{fig:motivation-regimes} are per second and are not representative
of the actual active keyspace; the number of active keys is larger than 100, as
some keys may be accessed at time \(t_0\), not in \(t_1\), and then again in
\(t_2\). Because the cache is too small, reads and writes hit rest of the
storage hierarchy and the excessive traffic triggers a LevelDB compaction on
the persistent database.  To avoid overloading the storage hierarchy with
requests, we design a multi-part policy that switches between:

@@

% results: same level of performance can be achieved 
The key observation is that small caches incur too much load on the persistent
database at the beginning of the run but should suffice after the initial read
flash crowd passes because the keyspace is far less active.  We program Mantle
to trigger the policy switch at 100K keys to absorb the flash crowd at the
beginning of the run. Once triggered, keys are evicted to bring the size of the
cache down to the threshold.  The actual policy is shown and described in more
detail in the next section in Figure~\ref{src:lru-dyn}.  The plot on the right
side of Figure~\ref{fig:methodology-tradeoff} shows the performance/utilization
trade-off of the multi-part policy, where the cache sizes for the \(n\) key
limit policy are along the \(x\) axis.  The performance and memory utilization
for a 100K key cache size is the same as the 100K bar in the ``Fixed Cache
Size" graph in Figure~\ref{fig:methodology-tradeoff} but the rest reduce the
size of the keyspace after the read flash crowd.  We see the worst performance
when the engine switches to the 10 key limit policy, which achieves 94\% of the
performance while only using 40KB of memory.

@@

The results in Figure~\ref{fig:methodology-tradeoff} are slightly deceiving for
two reasons: (1) segments take longer to generate later in the run and (2) the
memory footprint is the value at the end of 2.5 hours.  For (1), the trajectory
length vs.  wall-clock time curves down over time; as the nanoparticle grows it
takes longer to generate segments so by the time we reach 2 hours, over 90\% of
the trajectory is already generated.  For (2), the memory footprint rises until
we reach 100K key switch threshold at 0.4GB, as shown by the ``\(\Delta_1\),
Multi-Policy" curve in Figure~\ref{fig:memory-vs-time} but in
Figure~\ref{fig:methodology-tradeoff} we plot the final value. As a result, we
conclude that this policy only works well for this 2.5 hour run.

% but the result is still valid
Despite these caveats, the result is still valid: we found a multi-policy cache 
management strategy that absorbs the cost of a high read throughput on a small
keyspace and reduces the memory pressure for a 2.5 hour run. Our experiments
show the effectiveness of the policy engine we integrated into
ParSplice, not that we were able to identify the best policy for all system
setups ({\it i.e.} different ParSplice parameters, number of worker tasks, and
job lengths).  To solve that problem, we need a way to identify what thresholds
we should use for different configurations.

@@

\begin{figure*}[t!]
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
	\includegraphics[width=1\textwidth]{figures/keyspace-zoomed.png}\\
\caption{Key activity for a 4 hour run shows groups of accesses to the same
subset of keys. Detecting these access patterns leads to a more accurate cache
management strategy, which is discussed in
Section~\S\ref{sec:regime-detection}.\label{fig:keyspace-zoomed}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/dscache-vs-none.png}\\
	\caption{Performance/Utilization for dynamically sized cache (DSCache)
policy. With negligible performance degradation, DSCache adjusts to different
\(\Delta\)s over 2\(\times\) memory in the best case.
\label{fig:dscache-vs-none}}
    \end{subfigure}%
    \caption{Different cache management policies tested over the Mantle policy engine.}
\end{figure*}

@@

Figure~\ref{fig:keyspace-zoomed} shows which keys (\(y\) axis) are accessed by
tasks over time (\(x\) axis). The groups of accesses to a subset of keys occurs
because molecules are stuck in deep trajectories. Recall that the cache stores
the molecules' EOM minima, which is the smallest effective energy that a
molecule observes during its trajectory. So molecules stuck in deep
trajectories explore the same minima until they can escape to a new set of
states. This exploration of the same set of states is called a superbasin.  In
Figure~\ref{fig:keyspace-zoomed}, superbasins are never re-visited because the
simulation only adds molecules; we can never reach a state with less molecules.
This is why keys are never re-accessed.

Detecting these superbasins can lead to more effective cache management
strategies because the height of the groups of key accesses is ``how much" of
the cache to evict and the width of the groups of key accesses is ``when" to
evict values from the cache.  The zoomed portion of
Figure~\ref{fig:keyspace-zoomed} shows how a single superbasin affects the key
accesses. Moving along the \(x\) axis shows that the number of unique keys
accessed over time grows while moving along the \(y\) axis shows that early
keys are accessed more often.  Despite these patterns, the following
characteristics of superbasins make it hard to detect them:

@@

@@

  \item Calculus: use derivative to strip away magnitudes; use large positive
slopes followed by large negative slope as signal for new set of key accesses.
``Zero-crossing", set to 40 seconds, for distance between small/large spikes to
avoid false positives; ``window size", set to 200 seconds, for the size of the
moving average.

  \item K-Means Clustering fails because ``K" is not known {\it a-priori} and
groups of key accesses are different size. ``K", set to 4, for the number of clusters in the data
using the sum of the distances to the centroid.

  \item DBScan: finds clusters using density as a metric. ``Eps", set to 20, for
max distance between 2 samples in same neighborhood; ``Min", set to 5, for the
samples per core.

  \item Anomaly Detection: size of the image is too big and bottom edges are
not thick enough.

@@

After trying these techniques we found that the basic algorithm in
Figure~\ref{src:dyn-cache} works best. The algorithm detects groups of key
accesses, which we call ``fans", by iterating backwards through the key access
trace, finding the lowest key ID, and comparing against the lowest key ID we
have seen so far (Line 7). We also maintain the top and bottom of each group of
key accesses (Line 13) so we can tell the ``how much" policy the number of keys
to evict (Line 19).  The algorithm iterates backwards over the key access trace
because a change in the minimum value signals a new group of key accesses. No
signal exists iterating left to right, as the maximum value always increases
and the minimum values at the bottom of each group of key accesses are sparse.
For example, the maximum distance between values along the bottom edge of the
zoomed group of key accesses in Figure~\ref{fig:keyspace-zoomed} is 125
seconds, while the maximum distance between minimum values for the group of key
accesses before is 0 seconds. As a result of this sparseness, iterating left to
right requires a ``window size" parameter to determine when we think a minimum
value will not show up again.  The algorithm is O(\(n\)), where \(n\) is the
number events, but the benefit is that the approach avoids adding new
thresholds for key access pattern detection ({\it e.g.}, space between key
accesses, space between key IDs, and window size of consecutive key accesses).

@@

\begin{figure}[h]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
d = timeseries()
ts, id = d:get(d:size())
fan  = {start=nil, finish=ts, top=0, bot=id}
fans = {}
for i=d:size(),1,-1 do     -- iterate backwards
  ts, id = d:get(i)
  if id < fan['bot'] then  -- found a new fan!
    fan['start']  = ts
    fans[#fans+1] = fan 
    fan = {start=nil, finish=ts, top=0, bot=id}
  end

  if id > fan['top'] then  -- track top of fan
    fan['top'] = id 
  end 
end
fan['start'] = 0 
fans[#fans+1] = fan

if #fans < 2 then -- do not evict current fan
  return false 
else
  WRstate(fans[#fans-1]['top']-fans[1]['bot'])
  return true
end
\end{minted}
\caption{The dynamically sized cache policy, whose performance is shown in 
Figure~\ref{fig:cache-management}, iterates backwards over timestamp-key pairs
and detects when key accesses move on to a new subset of
keys ({\it i.e.} ``fans"). \label{src:dyn-cache}}
\end{figure}

### 2017-11-27 paper/sections/5_file-systems.tex
paper: addresses #35, #44, #46
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The cache management policies we developed earlier can be used by load
balancing policies to effectively spread load across a cluster. For example,
many distributed file systems spread the hierarchical namespace across a
dedicated metadata cluster and caching policies could be used to determine what
metadata to move and when to move it. To demonstrate this idea, consider
Figure~\ref{fig:trace-atime}, where the dots are the file system metadata reads
in a 1 hour window of a 3-day Lustre namespace trace and the vertical lines are
the groups of accesses detected by our policy from
Section~\S\ref{sec:regime-detection}.  The \(x\) axis is time and the \(y\)
axis is the file ID, where the file IDs are listed in the order that they
appear in the trace.  The trace is anonymized so all file names are replaced
with a unique identifier and we do not know what clients are doing.  Although
other access pattern detection algorithms are possible, we use the one designed
for cache management in Section~\S\ref{sec:regime-detection} without
modification and it successfully detects the largest group of key accesses that
starts at time 1000 seconds and ends at time 2200 seconds. File systems that
load balance file system metadata across a cluster would want to keep metadata
in that group of key accesses on the same server to reduce RPCs.

% burstiness of creates then compile
Cache management can also increase the capacity of a single server, which
affects how load should be distributed across a cluster.  For example, CephFS
clients and servers maintain a consistent cache so that the client can do
operations locally without contacting the metadata server.  But large caches
use more memory, so having smart policies that detect key access patterns would
greatly reduce memory footprints. For example, Figure~\ref{fig:compile-ops}
shows the trace of metadata requests for compiling code in CephFS.  The \(y\)
axis is  the number of file system metadata requests serviced by the metadata
server when uncompressing (\texttt{untar}), compiling (\texttt{make}), and
deleting (\texttt{rm}) the source code for the Linux kernel. If the system
knows that the job phases would progress from many creates, to many lookups, to
many deletes, then it could size its caches accordingly. For example, the file
system could cache none of the metadata from the \texttt{untar} phase and run
key access pattern detection during the \texttt{make} phase, resulting in the
metadata server/clients only caching metadata that is repeatedly used. For the
job in Figure~\ref{fig:compile-ops}, this would fill up the cache to only 20K
inodes (the unit of metadata for file systems) instead of 60K, resulting in
almost 40MB of memory savings (since an inode is about
1KB\footnote{http://docs.ceph.com/docs/master/dev/mds\_internals/data-structures/})
without sacrificing performance.

%- strategy: cache all inodes on create
\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/compile-ops.png}\\
\caption{File system metadata requests for a compile job show workload phases
characterized by a dominant request type ({\it e.g.}, creates for ``untar").
Using ParSplice cache management policies for these types of workloads would
reduce memory pressure without sacrificing performance.
\label{fig:compile-ops}}
\end{figure}

@@

  \item QoS: when to move clients, where to move clients, how much of the
reservation to move

  \item Scheduling: how much of a resource to allocate; more than just LRU
(RAD)

  \item Batching: how many operations to group together and when to send large
batches of updates

  \item Prefetching: how much to prefetch and how to select data to reterive
(forward/backward/stride detection algorithms for prefetching,

>>>>

The cache management policies we developed earlier can be used by load
balancing policies to effectively spread load across a cluster. For example,
many distributed file systems spread the hierarchical namespace across a
dedicated metadata cluster and caching policies could be used to determine what
metadata to move and when to move it. To demonstrate this idea, consider
Figure~\ref{fig:trace-atime}, where the dots are the file system metadata reads
in a 1 hour window of a 3-day Lustre namespace trace and the vertical lines are
the groups of accesses detected by our policy from
Section~\S\ref{sec:regime-detection}.  The \(x\) axis is time and the \(y\)
axis is the file ID, where the file IDs are listed in the order that they
appear in the trace.

The trace is anonymized so all file names are replaced with a unique identifier
and we do not know what clients are doing.  Although other access pattern
detection algorithms are possible, we use the one designed for cache management
in Section~\S\ref{sec:regime-detection} with slight modifications based on our
knowledge of file systems~\footnote{We filtered requests key ids less than
2000, as these are most likely path traversal requests to higher parts of the
namespace, {\it i.e.} root directories.} and it successfully detects the
largest group of key accesses that starts at time 1000 seconds and ends at time
2200 seconds. File systems that load balance file system metadata across a
cluster would want to keep metadata in that group of key accesses on the same
server to reduce RPCs.

%% burstiness of creates then compile
%Cache management can also increase the capacity of a single server, which
%affects how load should be distributed across a cluster.  For example, CephFS
%clients and servers maintain a consistent cache so that the client can do
%operations locally without contacting the metadata server.  But large caches
%use more memory, so having smart policies that detect key access patterns would
%greatly reduce memory footprints. For example, Figure~\ref{fig:compile-ops}
%shows the trace of metadata requests for compiling code in CephFS.  The \(y\)
%axis is  the number of file system metadata requests serviced by the metadata
%server when uncompressing (\texttt{untar}), compiling (\texttt{make}), and
%deleting (\texttt{rm}) the source code for the Linux kernel. If the system
%knows that the job phases would progress from many creates, to many lookups, to
%many deletes, then it could size its caches accordingly. For example, the file
%system could cache none of the metadata from the \texttt{untar} phase and run
%key access pattern detection during the \texttt{make} phase, resulting in the
%metadata server/clients only caching metadata that is repeatedly used. For the
%job in Figure~\ref{fig:compile-ops}, this would fill up the cache to only 20K
%inodes (the unit of metadata for file systems) instead of 60K, resulting in
%almost 40MB of memory savings (since an inode is about
%1KB\footnote{http://docs.ceph.com/docs/master/dev/mds\_internals/data-structures/})
%without sacrificing performance.
%
%%- strategy: cache all inodes on create
%\begin{figure}[t]
%\noindent\includegraphics[width=0.5\textwidth]{figures/compile-ops.png}\\
%\caption{File system metadata requests for a compile job show workload phases
%characterized by a dominant request type ({\it e.g.}, creates for ``untar").
%Using ParSplice cache management policies for these types of workloads would
%reduce memory pressure without sacrificing performance.
%\label{fig:compile-ops}}
%\end{figure}

@@

  \item QoS: when to move clients, where to move clients, how much of the
reservation to move. We could use Mantle to implement something like the
reservation algorithms based on utilization and period in
Fahrrad~\cite{povzner_horizon_2010} to achieve better guarantees without
sacrificing performance.

  \item Scheduling: when to yield computation cycles to another process, how
much of a resource to allocate. We could use Mantle to implement something like the RBED
scheduler~\cite{brandt:rtss2003-rad}, that separates resource allocation from
timing of delivery to enable real-time and non-real-time-scheduling classes.

  \item Batching: how many operations to group together and when to send large
batches of updates. We could use Mantle to shape the batching policies in the
shared resource interface in  Malacology~\cite{sevilla:eurosys17-malacology}.

  \item Prefetching: how much to prefetch and how to select data to retrieve.
We could use Mantle to implement forward/backward/stride detection algorithms
for prefetching in RAID arrays or something more complicated, like the time
series algorithms for adaptive I/O prefetching presented
in~\cite{tran:sc01-arima}.
